%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\usepackage[left=0.40in,top=0.3in,right=0.55in,bottom=0.2in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Qi(Tommy) Shu} % Your name 


\address{
\faGithub{ \href{https://github.com/qstommyshu}{qstommyshu}}\quad
\faLinkedin{ \href{https://www.linkedin.com/in/qi-shu/}{Qi(Tommy) Shu}}\quad
\faEnvelope{ \href{mailto:qstommyshu@gmail.com}{qstommyshu@gmail.com}}\quad
\faPhone(365)-888-0060}
% \address{} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE 
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
{\bf TD Securities} \hfill {\em May 2022 - Aug 2022} 
\\{\textit{Intern,Software Developer}}
% \\- Designed and wrote End-to-End UI automation test for team product release in an Agile development environment.
% \\- Implemented a system validating parquet files extracted from AWS S3 against CSV files from API, increased testing efficiency by 30\%.
% \\- Improved upon a large existing Java and Angular codebase by increasing test coverage and fixing bugs.
% \\- Worked on building a Business Intelligence MicroService, boosted revenue by 8\%.
\\- Enabled application specific query capability on internal tooling services.
\\- Enabled users to generate financial report automatically using GraphQl.
\\- Researched on graph database POC and migreated multiple microServices from mongoDB  to neo4j.
\\- Skills/Tools: \emph{Java(Spring), JavaScript(Node.js), Monogodb, Neo4j, Elixir, GraphQl}

{\bf CaseWare International} \hfill {\em May 2021 - May 2022} 
\\{\textit{Intern,Software Developer \& Software Developer in Test(May 2021 - Sep 2021)}}
\\- Designed and wrote End-to-End UI automation test for team product release in an Agile development environment.
\\- Implemented a system validating parquet files extracted from AWS S3 against CSV files from API, increased testing efficiency by 30\%.
\\- Improved upon a large existing Java and Angular codebase by increasing test coverage and fixing bugs.
\\- Worked on building a Business Intelligence MicroService, boosted revenue by 8\%.
\\- Skills/Tools: \emph{Java(Spring, Mockito), TypeScript(Angular, Cypress.io), NoSQL, AWS}

{\bf Lexivalley, Inc. } \hfill {\em Sep 2019 - Aug 2020} 
\\{\textit{Intern, Software Developer}}
\\- Reconstructed the old website, added Login/Authentication system, Email verification and Payment system.
\\- Developed the backend system, Database and crafted web flow, and deployed it using GCP, increased visitors by 50\%.
\\- Skills/Tools: \emph{Python(Flask), JavaScript, HTML/CSS, Google Cloud Platform, Git, MySQL}

\end{rSection}

%--------------------------------------------------------------------------------
%    Projects
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}

{\bf Flask blog}
\\- A full stack blog web application.
\\- Used SQLAlchemy to handle account and posts' data.
\\- Skills/Tools: \emph{Python(Flask), SQLAlchemy, JavaScript, HTML/CSS, OOP, REST API}

{\bf 2048 Game}
\\- A 2048 Game programmed in Java following OOD and MVC patterns. Covered with Unit Testing.
\\- Skills/Tool: \emph{Java(Swing), Junit, MVC, Object-Oriented Design}

{\bf COVID-19 Info Tracker}
\\- An application that tracks local COVID-19 spreading information based on user's IP address.
\\- Used Machine Learning libraries to predict future spreading based on data from external API.
\\- Skills/Tools: \emph{Python(Flask, Pytorch), REST API, Machine Learning}

% {\bf Fit-anywhere}
% \\-An all-platform mobile app that generates personalize training and eating habits based on user input.
% \\- Skills/Tools: \emph{Dart, REST API}

% {\bf Machine Learning and Deep Learning Models}
% \\- Implemented several ML models from ground up to better understand ML, such as Perceptron, MLP, and Regressions.
% \\- Skills/Tools: \emph{Calculus, Linear Algebra, Statistics, Python}

{\bf Exact Match}
\\- A Python tool with GUI to compare exact match of two csv files regardless the data order.
\\- Skills/Tool: \emph{Python(Pandas, Tkinter)}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf McMaster University } \hfill {\em Sep 2019 - April 2023} 
\\{ \textit {Computer Science (Co-op) B.A.Sc  }} \hfill{\em cGPA 3.9 / 4.0}
\begin{itemize}
    \item Extra Curriculum: Competitive programming club, Google Student Developer Club, Robomaster, AI Society.
    \item Honours/Awards: 2$^{nd}$ Place in Isaac Data Science Case Competition(2021), McMaster Engineering Competition Finalist(2020), Dean's Honor List(2020-2021), President Scholarship(2019).
\end{itemize}

\end{rSection}

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\textbf{Python, Java, JavaScript, TypeScript, Dart, Bash, SQL/NoSQL, Linux/Unix, HTML/CSS, Git, \LaTeX, REST API}\\
\textbf{React, Angular, Flask, MySQL, Pytorch, Doxygen, Google Cloud, AWS, Agile, Design Patterns, MicroServices}\\
% Programming: \ & aaa,bbb,ccc,ddd,eee,fff,ggg,hhh \\
% Software \& Tools: & {\textbf{Backend: }}qqqq,wwww,eeee,rrrr,tttt,yyyy,uuuu,iiii\\
% & {\textbf{FrontEnd: }}aaaaa,bbbbb,eeee,cccc\\
% & {\textbf{Others: }}uuuu,uyyy,oooo,aaaa,vvv,eeee
\end{tabular}

\end{rSection}

\end{document}